---
title: "Getting Started"
author: "Hannah Mandell"
date: "1/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Source: https://thebioengineer.github.io/tidytuesdayR/ 
Author: Ellis Hughes

{tidytuesdayR} has the main goal to make it easy to participate in the weekly #TidyTuesday project. Currently this is done by assisting with the import of data posted on the R4DataScience Tidy Tuesday repository.

Installation
This package is available on CRAN via:

```{r installation}
install.packages("tidytuesdayR")
```

To get the latest in-development features, install the development version from GitHub:

```{r}
#install.packages("remotes")
remotes::install_github("thebioengineer/tidytuesdayR")
```

Usage
There are currently two methods to access the data from the respository.

Load the Data!
The simplest way is to use the ‘tt_load()’ function. This function has accepts two types of inputs to determine which data to grab. It can be a date as a string in the YYYY-MM-DD format like below.

```{r load data}
library(tidytuesdayR)
# insert desired date
tt_data <- tt_load("2021-01-26")

# or you can use this method:
tt_data <- tt_load(2019, week = 3)
```

tt_load() naively downloads all the data that is available and stores them in the resulting tt_data object. To access the data, use the $ or [[ notation and the name of the dataset.

```{r accessing data in the tt_data object}
tt_data$agencies
tt_data[["agencies"]]
```

To view the readme, either print the tt_data object or use the readme() function. When you print the tt_data object, you also get the available datasets names printed in the console.

```{r viewing the readme}
readme(tt_data)
print(tt_data)
```

```{r the console should show the available datasets like such}
## Available Datasets:
##  agencies 
##  launches 
## 
```

TidyTemplate

As part of the goal of making participating in #TidyTuesday easier, {tidytuesdayR} now also provides a template! To use it, just use the use_tidytemplate() function!

By default, the template will assume to be using the most recent TidyTuesday. However, you can pass a date object or character string in YYYY-MM-DD format defining a different date you want to use. If you don’t recall the exact date, no worries, you can use the tt_available() function to figure out which date and get the date to use!

```{r}
## this weeks TidyTuesday!
tidytuesdayR::use_tidytemplate()

## TidyTuesday from Week 42 of 2019
tidytuesdayR::use_tidytemplate(refdate = "2021-01-26")
```

Additionally, by default the template will create the new file in your working directory, using the “YYYY_MM_DD” format per good practices. However, if you are so inclined, you can rename it to whatever you wish.

```{r renaiming the tidytuesday file if so desired}
tidytuesdayR::use_tidytemplate(name = "My Super Great TidyTuesday.Rmd")
```

