---
title: 'Transit'
output: html_document
date: '2021-01-05'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(tidytuesdayR)
library(lubridate)
library(dplyr)
library(tidyr)
#install.packages("countrycode")
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}
transit <- readr::read_csv("transit_cost.csv")

```



# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

transit %>% 
  map(glimpse)

head(transit)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

# write the data to a csv file
write.csv(transit, "transit_cost.csv", )

transit <- readr::read_csv("transit_cost.csv")  %>% 
  mutate(real_cost = as.numeric(real_cost), start_year = as.numeric(start_year)) %>%
  filter(!is.na(line)) %>%
  mutate(region = countrycode(country, origin = "ecb", destination = "region")) %>%
  mutate(region = case_when(country == "UK" ~ "Europe & Central Asia", TRUE ~ region))
```

```{r}
head(transit)
```

```{r}
tail(transit)
```

```{r}
transit %>%
  group_by(country) %>%
  summarize(mean(real_cost))
```

```{r}
# looking at the average real cost by country
tapply(transit$real_cost, transit$country, mean)
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

transit %>%
  ggplot(aes(x = start_year, y = real_cost, color = as.factor(rr)) ) + 
  geom_point() +
  scale_color_manual(values = c("#999999", "#E69F00", "#569BBD"), 
                       name = "Railroad",
                       breaks = c(0, 1, NA),
                       labels = c("not railroad", "railroad", "missing"))
```
```{r}
# non-railroad vs railroad counts
table(transit$rr)
```

```{r}
transit %>%
  ggplot(aes(x = length, y = real_cost, color = region) )+ 
  geom_point() 
```

```{r}
transit %>%
  ggplot(aes(y = real_cost, x = region, color = region)) + 
  geom_boxplot() 
```


```{r}
library(knitr)
```

