---
title: "Art and Artists"
author: "Hannah Mandell"
date: "1/12/2021"
output:
  html_document: default
  pdf_document: default
---

The data today come from the Tate Art Gallery 
(https://github.com/tategallery/collection)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(tidytuesdayR)
library(lubridate)
library(dplyr)
library(tidyr)
library(broom)
library(countrycode)
library(praise)
#install.packages("tidymodels")
library(tidymodels)
#install.packages("ranger")
```

```{r starting off the day right}
praise()
```

# Get the Data
```{r}
tt_data <- tt_load("2021-01-12")

# make and save csvs
artwork <- tt_data$artwork
write_csv(artwork, "artwork.csv")
artists <- tt_data$artists
write_csv(artists, "artists.csv")

```

# Preliminary looks at the data
```{r head}
head(artwork)
```

```{r glimpse}
glimpse(artwork)
```

```{r }
head(artists)
```

```{r}
glimpse(artists)
```

Note: over half of the pieces are by Joseph Turner! We might be interested in analyzing the data without his work. 

```{r}
artwork %>%
  group_by(artistId) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  head()

artists %>%
  filter(id == 558)
  

```

Both `placeofBirth` and `placeofDeath` are given as City, Country. Let's look to split these into different categories - it might make it easier to analyze or model the data. 

```{r splitting city & country by comma}
artists <- artists %>%
  separate(placeOfBirth, c("cityBirth", "countryBirth"), sep = ", ", fill = "left") %>%
  separate(placeOfDeath, c("cityDeath", "countryDeath"), sep = ", ", fill = "left")

artists %>% select(countryBirth) %>% table()
```

```{r boxplot of country & year of artwork}
artists %>%
  group_by(countryBirth) %>%
  mutate(count = n()) %>%
  filter(count >= 10) %>%
  ungroup() %>%
  ggplot(aes(x = countryBirth, y = yearOfBirth)) +
  geom_boxplot()

```


# Joins!
Combining datasets with shared unique identifiers:
Inner Join = keep everything that is shared in both datasets
Full Union = keep everything from each dataset

Let's combine the datasets so that if we want to use gender to ask questions about the art, the information is available!

```{r}
artartist1 <- 
  inner_join(artists, artwork, by = c("id" = "artistId"))

artartist2 <- 
  full_join(artists, artwork, by = c("id" = "artistId"))

nrow(artwork)
nrow(artartist1)
nrow(artartist2)
  
```
Some inportant insights from these runs:

There are 6 pieces of art that do not have a listed artist. They are left out in the intersect. 

There are ALSO 194 artists in the dataset that do not have artwork in the database, and that is why we get MORE data in artartist2 than in artwork itself. 

# Visualization

```{r}
artwork %>%
  select(artistRole) %>%
  table()

#density plot
artartist1 %>%
  filter(id != 558) %>%
  ggplot(aes(x = year, color = gender)) + 
  geom_density()

#histogram
artartist1 %>%
  filter(id != 558) %>%
  ggplot(aes(x = year, color = gender, fill = gender)) + 
  geom_histogram()
  
```

We see that the relative proportion of female artwork increases as we turn towards modern times. Removing artist # 558 helps remove his skew. 

# Random Forest Model
Let's explore a RFM. 

```{r}
#install.packages('ranger')
```


```{r}

set.seed(47)
library(tidymodels)
library(vip)


# remove the artist that is listed an enormous number of times 
# because he might skew the data
artRF <- artartist1 %>%
  filter(id != 558)

# 75% train, 25% test
data_split <- initial_split(artRF, prop = 0.75)


art_train <- training(data_split)

# for better data science, we would perform more analysis on these
# individual fields, but removing them is sufficient for our low-stakes 
# purposes now
art_test  <- testing(data_split) %>%
  filter(!is.na(gender)) %>%
  filter(!is.na(width)) %>%
  filter(!is.na(height)) %>%
  filter(!is.na(acquisitionYear)) %>%
  filter(!is.na(yearOfBirth)) %>%
  filter(!is.na(yearOfDeath))

# give it the right fields to look at
# birth and death year might make the model overfit to the training data
rand_forest(mode = "regression") %>% 
   set_args(importance = "permutation") %>%
   fit(year ~ gender + width + height + acquisitionYear +
         yearOfBirth + yearOfDeath, 
       data = art_train) %>% 
   vip::vip() 

```
We see that the model is relying very heavily on `yearOfBirth` and `yearOfDeath` to make its predictions, as we hypothesized. 

```{r}
rand_forest(mode = "regression") %>% 
   fit(year ~ gender + width + height + acquisitionYear +
         yearOfBirth + yearOfDeath, data = art_train) %>% 
   predict(new_data = art_test) %>%
   ggplot(aes(y = .pred, x = art_test$year)) + 
   geom_point() +
   geom_abline(intercept = 0, slope = 1) +
  ylab("Predicted Year") +
  xlab("Year of Creation")
```
The above graph shows that our model has a very high accuracy - probably too accurate.
